Supplementary Material for Asymmetry paper

### 2020-05-11 Supplementary/Sup_mat.Rmd
Sup mat updated

We started by fitting a a beta distribution to the _Throwing Experiment_ data from Clarke and Hunt (2016) using the `fitdistrplus` package, as illustrated in Figure 1a. The fit with the empirical data is reasonable, although we under-estimate the frequency of standing positions $\sim0$.

@@

```{r load in data and draw distributions, include = T, echo = F}
# so we're interested in the difference between the closest and furthest... 
# so we should just plot that? 
load("../power/Money_and_two/scratch/df_sample")
load("../power/Money_and_two/scratch/df_all")
plt_data <- df_all %>%
  filter(standard_lab %in% c("10%","90%")) %>%
  group_by(participant, condition, standard_lab) %>% 
  summarise(norm_pos = mean(norm_pos)) %>%
  ggplot(aes(standard_lab, norm_pos,
             colour = condition,
             fill = condition)) + 
  geom_boxplot(alpha = .3) + 
  geom_point(alpha = .3, position = position_jitterdodge(.1)) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  scale_y_continuous("Normalised Placement") +
  theme(axis.title.x = element_blank()) + 
  guides(colour = guide_legend(title = "Condition"),
         fill = guide_legend(title = "Condition"))

>>>>

We started by fitting a a beta distribution to the _Throwing Experiment_ data from Clarke and Hunt (2016) using the `fitdistrplus` package, as illustrated in Figure \@ref(fig:drawdistributions) (left panel). The fit with the empirical data is reasonable, although we under-estimate the frequency of standing positions $\sim0$.

@@

```{r Exp2and3Plots, include = T, echo = F, fig.cap="The top plot shows boxplots for the empirical data being sampled from. The bottom plots show the 95% HDI for the difference in the close (90%) and far (10%) separations"}
# so we're interested in the difference between the closest and furthest... 
# so we should just plot that? 
load("../power/Money_and_two/scratch/df_sample")
load("../power/Money_and_two/scratch/df_all")
plt_data <- df_all %>%
  filter(standard_lab %in% c("10%","90%")) %>%
  group_by(participant, condition, standard_lab) %>% 
  summarise(norm_pos = mean(norm_pos)) %>%
  ggplot(aes(standard_lab, norm_pos,
             colour = condition,
             fill = condition)) + 
  geom_boxplot(alpha = .3) + 
  geom_point(alpha = .3, position = position_jitterdodge(.1)) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  scale_y_continuous("Normalised Placement") +
  theme(axis.title.x = element_blank()) + 
  guides(colour = guide_legend(title = "Condition"),
         fill = guide_legend(title = "Condition"))
